\section{Introduction} 
This project is an extension of my thesis, \href{"https://academicworks.cuny.edu/cgi/viewcontent.cgi?article=1682\&context=hc_sas_etds"}{ A Study of CUSUM Statistics on Bitcoin Transactions}, where I was tasked with implementing CUSUM statistic processes to identify price actions periods in bitcoin markets. After developing a tool for market orders, the natural extension was to find relationships from activities in the limit order book. I started developing this tool to record instances of the limit order book in order to record Limit Order insertions (LO), cancellations (CO), and Market Orders (MO).

As the project grew I wanted to make a tool that could be used by academics looking to apply and develop market microstructure models in live markets. As a result, the styles in which the limit order book and order book events are recorded are being developed in accordance to the conventions presented in recent market microstructure papers correspond to the following papers:
\begin{enumerate}
	\item \href{https://arxiv.org/pdf/1312.0563.pdf}{Huang W., Lehalle C.A. and Rosenbaum M. - Simulating and analyzing order book data:The queue-reactive model}\cite{Huang:2020}
	\item \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.139.1085\&rep=rep1\&type=pdf}{Cont R., Stoikov S. and Talreja R. - A stochastic model for order book dynamics}\cite{ContStoikovTalreja2009:StochModelOBD}
	
	\item \href{https://arxiv.org/pdf/1011.6402.pdf}{Cont R., Kukanov A. and Stoikov S. - The price impact of order book events}\cite{ContKukanovStoikov2012:PriceImpactOBE}
	
	\item \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3431139}{Cartea. A, Jaimungal S. and Wang Y. - Spoofing and Price Manipulation in Order Driven Markets}\cite{CarteaJaimungalWang2020:SpoofingPriceManipulation}
	
	\item \href{https://link.springer.com/article/10.1007/s42521-019-00007-w#article-info}{Silyantev, E. - Order flow analysis of cryptocurrency markets}\cite{Silyantev2019:Orderflowanalysis}\footnote{This paper shows a working model implementing Order Flow Imbalance (OFI) and Trade Flow Imbalance(TFI) to BTC-USD trades was done by \href{https://medium.com/@eliquinox/order-flow-analysis-of-cryptocurrency-markets-b479a0216ad8}{Ed Silyantev}. He developed a tool to assess OFI and TFI of XBT-USD pair. }
\end{enumerate}

\newpage
\section{crobat Features} 

\subsection{Orderbook updating}
\begin{itemize}
	\item Order book recording module that maintains a time-series of:
	\begin{enumerate}
		\item Limit order insertions, cancellations and market orders,
		\item volumes at $n^{\textrm{th}}$ best limits, and
		\item prices at  $n^{\textrm{th}}$ best limits.
	\end{enumerate}
	\item Outputs these time-series objects as .xlsx files.
\end{itemize}

\newpage

\section{Getting Started and Installation}

\subsection{CoPrA}

\subsection{Installation}

This project is a work in progress. I suggest you fork the project, and clone to your local environment. The file \texttt{csv\_out.py} located in crobat/crobat/test/ will contain a basic testing environment for a set length. 
\medskip
\hrule
\smallskip
\noindent \textbf{Note:} crobat is not an optimized order book implementation and may not be I/O bound. This suboptimality is due to frequent scanning of all prices for insertion forces the complexity to be greater than $\sim O(n)$ for $n$ being the length of the snapshot being iterated over. You may find that depending on the popularity of the asset and the computational power of your PC, you may run into errors arising from the computer not being able to keep up with the market (especially BTC-USD). I would suggest experimenting with an unpopular pair, (e.g.,  XRP-USD), or a crypto-crypto pair (e.g., XRP-BTC), and timing your queries outside of NYSE, and London Stock Exchange trading hours as they tend to have less activity.
\smallskip
\hrule
however if you want an easy installation: 

```pip3 install crobat``` 

\newpage